Plots for Latent Hawkes Paper

### 2021-08-10 output_scripts/Paper_Plots.Rmd
rerun all paper plots with half normal prior results for c-mmhp models

# don't write to this path
data_path <- "../output/revisions/lapl_check/"

@@

for (s in sims) {
  print(s)
  load(paste0(sim_data_path, "sim_model3_fit123_", s, ".RData"))
  load(paste(sim_data_path, "fit123_state_est_", s, ".RData", sep = ""))
  clean_sim_data <- cleanSimulationData(
    raw_data = sim_model3_data,
    cut_off = cut_off,
    N = length(object_par$f_vec_1)
  )

@@

```{r log-p-value}
cols_plot <- col_df %>% 
  filter(method %in% c("C-HP","C-DCHP","C-MMHP", "True")) %>%
  arrange(factor(method, levels = c("C-HP", "C-DCHP", "C-MMHP", "True"))) %>%
  pull(cols)

@@

```{r fig-6a-rank-vs-isi}
### Rank Comparison for Single Cohort ####
current_cohort <- 5
# data_path

@@

This has not finished for new simulation setting yet.

>>>>

# don't write to this path
data_path <- "../output/revisions/lapl_check/prior_check/"

@@

for (s in sims) {
  # print(s)
  load(paste0(sim_data_path, "sim_model3_fit123_", s, ".RData"))
  load(paste(sim_data_path, "fit123_state_est_", s, ".RData", sep = ""))
  clean_sim_data <- cleanSimulationData(
    raw_data = sim_model3_data,
    cut_off = cut_off,
    N = length(object_par$f_vec_1)
  )

@@

```{r log-p-value, eval=FALSE}
cols_plot <- col_df %>% 
  filter(method %in% c("C-HP","C-DCHP","C-MMHP", "True")) %>%
  arrange(factor(method, levels = c("C-HP", "C-DCHP", "C-MMHP", "True"))) %>%
  pull(cols)

@@

```{r fig-6a-rank-vs-isi}
### Rank Comparison for Single Cohort ####
current_cohort <- 5
# want to update this now
# data_path

@@
